Removal and Replacement only

### 2020-08-07 analysis/boneyard.Rmd
rm facet_wrap

>>>>

## tsne

```{r tSNE}

# removal
hyptsne <- subsetmaketsne("hypothalamus", removallevels, sexlevels)
pittsne <- subsetmaketsne("pituitary", removallevels, sexlevels)
gontsne <- subsetmaketsne("gonads", removallevels, sexlevels)

pittsne <- addgroupings(pittsne)

t4 <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors) +  labs(title = "pituitary ", subtitle = "parental stage and manipulations") +
  facet_wrap(~sex) 
t5 <- plottsneelipsev2(pittsne, pittsne$extint, colorhypothesis) +  labs(title = "  ", subtitle = "external enviornment")   +
  facet_wrap(~sex) + theme(axis.title.y = element_blank())
t6 <- plottsneelipsev2(pittsne, pittsne$earlylate, colorhypothesis) +  labs(title = "  ", subtitle = "internal clock")   +
  facet_wrap(~sex) + theme(axis.title.y = element_blank())
t456 <- plot_grid(t4, t5, t6, nrow = 1, rel_widths = c(1.1,1,1))
t456

# replacement
hyptsne <- subsetmaketsne("hypothalamus", timinglevels, sexlevels)
pittsne <- subsetmaketsne("pituitary", timinglevels, sexlevels)
gontsne <- subsetmaketsne("gonads", timinglevels, sexlevels)

pittsne <- addgroupings(pittsne)

t4 <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors) +  labs(title = "pituitary ", subtitle = "parental stage and manipulations") +
  facet_wrap(~sex) 
t5 <- plottsneelipsev2(pittsne, pittsne$extint, colorhypothesis) +  labs(title = "  ", subtitle = "external enviornment")   +
  facet_wrap(~sex) + theme(axis.title.y = element_blank())
t6 <- plottsneelipsev2(pittsne, pittsne$earlylate, colorhypothesis) +  labs(title = "  ", subtitle = "internal clock")   +
  facet_wrap(~sex) + theme(axis.title.y = element_blank())
t456 <- plot_grid(t4, t5, t6, nrow = 1, rel_widths = c(1.1,1,1))
t456

## DEGs

```{r allDEGs}
DEG_path <- "../results/DEseq2/treatment/"   # path to the data
DEG_files <- dir(DEG_path, pattern = "*DEGs") # get file names
DEG_pathfiles <- paste0(DEG_path, DEG_files)
#DEG_files

allDEG <- DEG_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name") %>% 
  mutate(DEG = sapply(strsplit(as.character(file_name),'./results/DEseq2/treatment/'), "[", 2))  %>% 
  mutate(DEG = sapply(strsplit(as.character(DEG),'_diffexp.csv'), "[", 1))  %>% 
  mutate(tissue = sapply(strsplit(as.character(DEG),'\\.'), "[", 1)) %>%
  mutate(down = sapply(strsplit(as.character(DEG),'\\_'), "[", 3)) %>%
  mutate(up = sapply(strsplit(as.character(DEG),'\\_'), "[", 4)) %>%
  mutate(comparison = paste(down,up, sep = "_")) %>%
  mutate(sex = sapply(strsplit(as.character(sextissue),'\\_'), "[", 1)) %>%
  mutate(tissue = sapply(strsplit(as.character(sextissue),'\\_'), "[", 2)) %>%
  dplyr::select(sex,tissue,comparison, direction, gene, lfc, padj, logpadj) # %>%
 # mutate(tissue = factor(tissue, levels = tissuelevel),
  #       comparison = factor(comparison , levels = comparisonlevelsremoval),
  #       direction = factor(direction, levels = alllevels))
head(allDEG)

candidateDEGS <- allDEG %>%
  filter(gene %in% parentalcaregenes) %>%
  mutate(posneg = ifelse(lfc >= 0, "+", "-"),
         sex = recode(sex, "female" = "F", "male" = "M" ),
         tissue = recode(tissue, 
                         "hypothalamus" = "H",
                         "pituitary" = "P", 
                         "gonad" = "G", "gonads" = "G")) %>%
  mutate(res = paste(sex, tissue, posneg, sep = "")) %>%
  select(gene, res, comparison)  %>%
  group_by(gene,  comparison) %>%
  summarize(res = str_c(res, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = res) %>%
  select(gene, inc.d3_m.inc.d3, inc.d9_m.inc.d9, inc.d17_m.inc.d17, hatch_m.n2,
         inc.d17_prolong, hatch_prolong,extend_hatch, n5_extend, 
         early_inc.d9 ,hatch_early)
head(candidateDEGS[1:5])
```

## suppl fig 1

```{r supplfig-4}

comparisonlevelsmanip <- c("inc.d3_m.inc.d3", "inc.d9_m.inc.d9", "inc.d17_m.inc.d17", "hatch_m.n2",
         "early_inc.d9" ,"hatch_early", "inc.d17_prolong", "hatch_prolong","extend_hatch", "n5_extend")

# for fig 1
DEGmanip <- allDEG %>% 
  filter(comparison %in% comparisonlevelsmanip) %>%
  mutate(comparison = factor(comparison, levels = comparisonlevelsmanip))

DEGmanip %>% 
  group_by(comparison, sex, tissue) %>%
  summarize(totalDEGs = n())  %>%
  arrange(desc(totalDEGs))

s1a <- makebargraph(DEGmanip, "hypothalamus","DEGs w/ + LFC", 0, 3200, DEGmanip$comparison) + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) + 
  labs(subtitle = "hypothalamus") + geom_vline(xintercept = 4.5, linetype = "dashed", color = "grey")

s1b <- makebargraph(DEGmanip, "pituitary","DEGs w/ + LFC", 0, 3200, DEGmanip$comparison) + 
  theme(axis.text.x = element_blank(), axis.title.x = element_blank(), strip.text = element_blank()) + 
  labs(subtitle = "pituitary")  + geom_vline(xintercept = 4.5, linetype = "dashed", color = "grey")

s1c <- makebargraph(DEGmanip, "gonad","DEGs w/ + LFC", 0, 3200, DEGmanip$comparison) + 
  theme(strip.text = element_blank()) + 
  labs(subtitle = "gonad", x = "Comparison of parental stage and manipulation groups") + geom_vline(xintercept = 4.5, linetype = "dashed", color = "grey") + 
  scale_x_discrete(breaks= comparisonlevelsmanip,
                      labels= comparisonlevelsmanip,
                   drop=FALSE)

contrasts <- png::readPNG("../figures/images/fig_fig4sup1.png")
contrasts <- ggdraw() +  draw_image(contrasts, scale = 1)

supplfig3 <- plot_grid(contrasts, s1a, s1b, s1c, ncol = 1, rel_heights = c(0.5, 1,1,1.5))
supplfig3

pdf(file="../figures/supplfig-3-1.pdf", width=5, height=5)
plot(supplfig3)
dev.off()

write.csv(candidateDEGS, "../results/table2.csv", row.names = F)
```

### 2020-08-07 analysis/figure-3.Rmd
rm facet_wrap

---
title: "Fig3"
output: md_document
---

# Figure 3: All things prolactin

```{r setup}
library(tidyverse)
library(cowplot)
library(ggimage)
library(apaTables)
library(factoextra)
library(corrr)
library(ggpubr)
library(ggrepel)
library(ggsignif)
library(forcats)

@@

colData <- read_csv("../metadata/04_colData.csv") %>%
  filter(treatment %in% charlevels) %>%
  mutate(tissue = factor(tissue, levels = tissuelevels),
         treatment = factor(treatment, levels = charlevels),
         temprowname = V1) %>% 
  column_to_rownames(var = "temprowname") 
head(colData)
# check ready for analysis
# row.names(countData) == row.names(colData)
head(row.names(countData) == row.names(colData))
```

## PCA data

```{r PCA}
# pca relies on count data from limma
pca1f <- subsetmakepca("pituitary", charlevels, "female")	
pca2f <- makefvizdf("pituitary", charlevels, "female")

pca1m <- subsetmakepca("pituitary", charlevels, "male")	
pca2m <- makefvizdf("pituitary", charlevels, "male")

pca1 <- subsetmakepca("pituitary", charlevels, sexlevels)	
pca2 <- makefvizdf("pituitary", charlevels, sexlevels)	
```

## candidate genes, hypotheses genes, and data-driven genes

```{r}
# all genes lists in "./R/genelists.R"

# candidate counts for boxplots
candidatevsd <- read_csv("../results/06_candidatevsd.csv") %>%
  filter(treatment %in% charlevels) %>%
  mutate(treatment = factor(treatment)) %>%
  mutate(tissue = factor(tissue, levels = tissuelevel),
        treatment = factor(treatment, levels = charlevels)) %>%
  drop_na()
head(candidatevsd)

## prlpit
PRLpit <- candidatevsd %>% 
  filter(gene == "PRL", tissue == "pituitary")

# list of pvalue and DEGs
allDEG <- read_csv("../results/06_allDEG.csv")  %>%
  mutate(direction = factor(direction, levels = hypothesislevels))

# DEGs infor for PRL and external
hilodf <- allDEG %>%
  filter(comparison == "lo_hi")  %>%
  arrange(padj) 
hilogenes <- hilodf %>%  top_n(20) %>% pull(gene)

eggchickdf <- allDEG %>%
  filter(!comparison %in% c("lo_hi", "nest_eggs", "nest_chicks"))  %>%
  arrange(padj)  
eggchickgenes <- eggchickdf %>%  top_n(20) %>% pull(gene)

## data-driven PRL genes
pithilo <- makecorrdf("female", "pituitary", hilogenes)
pitWGCNA <- makecorrdf("female", "pituitary", WGCNAgenes[32:52])

## https://www.gynecologiconcology-online.net/article/S0090-8258(19)30069-1/fulltext
cancergenes <- makecorrdf("female", "pituitary", c(shaidgenes,suszynskaagenes, "PRL"))

## for scatter correlation (not currently usesed)
candidatevsdwide <- candidatevsd  %>%
    pivot_wider(names_from = gene, values_from = counts) 
pitwide <- subsetcandidatevsdwide(sexlevels, "pituitary")

## number of genes total vs plotted

eggchickdf %>% filter(tissue == "pituitary") %>% nrow()
hilodf %>% filter(tissue == "pituitary") %>% nrow()
length(WGCNAgenes)
```

```{r fig3, fig.width=7.25, fig.height=7.25}

a1 <- plotpc12(pca1, pca2, pca1$treatment, allcolors, "Pituitary gene expression", NULL)   
a2 <- plotprolactin(PRLpit, PRLpit$counts, "PRL", NULL) + 
  theme(axis.text.x = element_text(angle = 25))  +
  facet_wrap(~sex)
a <- plot_grid(a1,a2, labels = c("A", "B"), label_size = 8, rel_widths = c(1,1))

b1 <- png::readPNG("../figures/images/fig_fig3b.png")
b1 <- ggdraw() +  draw_image(b1, scale = 1)
b2 <- makenewbargraph("pituitary", "female","eggs_chicks", 0, 4000) + labs(subtitle = "female")  + labs(title = " ") +
  scale_x_discrete(labels = "eggs vs. chicks")
b3 <- makenewbargraph("pituitary", "male", "eggs_chicks", 0, 4000)  + labs(subtitle = "male")  + labs(title = " ") +
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank()) +
  scale_x_discrete(labels = "eggs vs. chicks")
b4 <- makenewbargraph("pituitary", "male", "lo_hi", 0, 4000)  +
  scale_x_discrete(labels = "lo vs. hi PRL")
b5 <- makenewbargraph("pituitary", "female", "lo_hi", 0, 4000)   + 
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank()) +
  scale_x_discrete(labels = "lo vs. hi PRL")
b25 <- plot_grid(b2,b3,b4,b5, nrow = 2, rel_widths = c(1.2,1), rel_heights = c(1.2,1))

b6 <-  plottopDEGs(eggchickdf, "female",  "LFC eggs vs. chicks", "Top 10 female DEGs") + labs(title = " ")
b7 <-  plottopDEGs(eggchickdf, "male",  "LFC eggs vs. chicks", "Top 10 male DEGs") + labs(title = " ")
b8 <-  plottopDEGs(hilodf, "female",  "LFC lo vs. hi PRL", NULL)
b9 <-  plottopDEGs(hilodf, "male",  "LFC lo vs. hi PRL", NULL)
b15 <- plot_grid(b1,b25,nrow = 1, rel_widths = c(1.2,1))
b69 <- plot_grid(b6,b7,b8,b9, align = "v" , rel_heights = c(1.2,1))
b <- plot_grid(b15,b69, labels = c("C"), label_size = 8, rel_widths = c(1.2,1))

c1 <- plotcorrplot(pithilo, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 DEGs, low vs. high PRL") 
c2 <- plotcorrplot(pitWGCNA, NULL) + theme(legend.position = "none") + labs(subtitle = "20 genes in WGCNA module with PRL") 
c3 <- plotcorrplot(cancergenes, NULL) + theme(legend.position = "right") + labs(subtitle = "Breast, ovary, & piuitary cancer genes") 
c <- plot_grid(c1,c2,c3, nrow = 1, labels = c("D"), label_size = 8, rel_widths = c(1,1,1.3))

fig3 <- plot_grid(a, b, c, nrow = 3, rel_heights = c(1.2,2,1.8))
fig3
```

```{r savefiles}
write.csv(PRLpit,"../results/PRLvsd.csv", row.names = F)

pdf(file="../figures/fig3-1.pdf", width=7.25, height=7.25)
plot(fig3)
dev.off()
```

```{r forvictoria, eval = F}
## PRL and PRLR in three tissues

candidatevsd <- candidatevsd %>%
  filter(treatment %in%  c("early", "extend", charlevels))

p1 <- candidateboxplot("hypothalamus", c("PRL"), sexlevels) + labs(subtitle = "hypothalamus", title = "PRL")
p2 <- candidateboxplot("pituitary", c("PRL"), sexlevels) + labs(subtitle = "pituitary")
p3 <- candidateboxplot("gonad", c("PRL"), sexlevels) + labs(subtitle = "gonads") + theme(axis.text.x = element_text(angle = 45))

p4 <- candidateboxplot("hypothalamus", c("PRLR"), sexlevels) + labs(subtitle = " ", title = " ") 
p5 <- candidateboxplot("pituitary", c("PRLR"), sexlevels) + labs(subtitle = " ")
p6 <- candidateboxplot("gonad", c("PRLR"), sexlevels) + theme(axis.text.x = element_text(angle = 45))+ labs(subtitle = " ")

plot_grid(p1,p4,p2,p5,p3,p6, ncol = 2, rel_heights = c(1.2,1,1.2))
```

>>>>

---
title: "Removal and Replacement only"
output: md_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(Rtsne)
library(ggsignif)
library(corrr)

@@

colData <- read_csv("../metadata/00_colData.csv") %>%
  mutate(treatment = factor(treatment, levels = alllevels),
         tissue = factor(tissue, levels = tissuelevels)) %>% 
  column_to_rownames(var = "X1") 
head(colData)
# check ready for analysis
# row.names(countData) == row.names(colData)
head(row.names(countData) == row.names(colData))
```

## variance stabilized gene expression  (vsd)

```{r vsd}
vsd_path <- "../results/DEseq2/treatment/"   # path to the data
vsd_files <- dir(vsd_path, pattern = "*vsd.csv") # get file names
vsd_pathfiles <- paste0(vsd_path, vsd_files)
vsd_files

allvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1") 
## before pivoting, check names of df with
## head(names(allvsd)) and tail(names(allvsd))
allvsd <- allvsd %>% 
  pivot_longer(cols = L.G118_female_gonad_control:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "samples", values_to = "counts") 
allvsd <- as_tibble(allvsd)
head(allvsd[2:4])
tail(allvsd[2:4])

```

```{r candidatevsd}

# for plotting gene expression over time
getcandidatevsdmanip <- function(whichgenes, whichtissue){

  candidates  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1),
                  sextissue = sapply(strsplit(sextissue, '../results/DEseq2/treatment/'), "[", 2),
                  sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4),
                treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1),
                treatment = recode(treatment, "m.hatch" = "m.n2", "extend.hatch" = "m.n2",
                                                   "inc.prolong" = "prolong", "m.inc.d8" = "early"),
                treatment =  factor(treatment, levels = alllevels),
                earlylate = fct_collapse(treatment, 
                                  early = c("early", "m.inc.d3", "m.inc.d9",
                                           "lay", "inc.d3", "inc.d9" ),

                                  late = c("inc.d17", "m.inc.d17", "prolong" ,  "hatch" , 
                                         "m.n2", "extend", "n5", "n9"),
                                  reference = c("control", "bldg")),
                extint = fct_collapse(treatment, 
                                  loss = c("m.inc.d3", "m.inc.d9", "m.n2", "m.inc.d17"),
                                  eggs = c("lay","inc.d3", "inc.d9", "inc.d17", "prolong"),
                                  chicks = c("early", "hatch", "extend", "n5", "n9"),
                                  reference = c("control", "bldg")))  %>%
    dplyr::select(gene, counts, sex, tissue, treatment, earlylate, extint, samples)  
  return(candidates)
}

candidatevsd <- getcandidatevsdmanip(candidategenes)

hypvsd <- candidatevsd %>% filter(tissue %in% "hypothalamus")  
pitvsd <- candidatevsd %>% filter(tissue %in% "pituitary") 
gonvsd <- candidatevsd %>% filter(tissue %in% "gonad")

hypvsdf <- candidatevsd %>% filter(tissue %in% "hypothalamus", sex == "female")  %>% drop_na()
pitvsdf <- candidatevsd %>% filter(tissue %in% "pituitary", sex == "female") %>% drop_na() 
gonvsdf <- candidatevsd %>% filter(tissue %in% "gonad", sex == "female")  %>% drop_na()

hypvsdm <- candidatevsd %>% filter(tissue %in% "hypothalamus", sex == "male")  %>% drop_na()
pitvsdm <- candidatevsd %>% filter(tissue %in% "pituitary", sex == "male") %>% drop_na()
gonvsdm <- candidatevsd %>% filter(tissue %in% "gonad", sex == "male") %>% drop_na()

# not all genes appear to be expressed in all tissues. added drop_na()
filter(gonvsd, treatment == "control") %>% head()
```

## candidate gene box plots

```{r fig3, fig.height=7.25, fig.width=7.25}
plotcandidatemanp <- function(df, whichgene, whichtissue){

  p <- df %>%
    dplyr::filter(gene  == whichgene)  %>%
    ggplot(aes(y =  counts, x = treatment, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA, lwd=0.5) +
    #facet_wrap(~sex) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "none",

          axis.text.x = element_text(angle = 45, hjust = 1),
          plot.subtitle = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(title = whichtissue, 
         subtitle = whichgene, 
         y = "gene expression", x = "Semi-sequential stages") +
    geom_signif(comparisons = list(c("inc.d9", "early"), 
                                  c( "inc.d17", "prolong"), 
                                  c( "prolong", "hatch")),
                map_signif_level=TRUE,
                textsize = 2, family = 'Helvetica',
                vjust = 0, size = 0.5, step_increase = 0.075) +
  geom_signif(comparisons = list(c( "inc.d3", "m.inc.d3"),
                                   c( "inc.d9", "m.inc.d9"),
                                   c( "inc.d17", "m.inc.d17"),
                                   c( "hatch", "m.n2")),
                map_signif_level=TRUE,
                textsize = 2, family = 'Helvetica',
                vjust = 0,  size = 0.5, step_increase = 0.075) +
    geom_signif(comparisons = list(c( "hatch", "extend"), 
                                  c( "n5", "extend")),
                map_signif_level=TRUE,
                textsize = 2, family = 'Helvetica',
                vjust = 0, size = 0.5, step_increase = 0.075)

  return(p)

}

boxplotextint <- function(df, whichgene, whichtissue){

  p1 <- df %>%
    dplyr::filter(gene  == whichgene)  %>%
    mutate(earlylate = factor(earlylate, levels = levelhypothesis)) %>%
    ggplot(aes(y =  counts, x = earlylate, fill = earlylate, color = sex)) +
    geom_boxplot(outlier.shape = NA, lwd=0.5) +
    #facet_wrap(~sex) +
    geom_jitter(size = 0.25, aes(color = treatment)) +
    theme_B3() +
  scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
  geom_signif(comparisons = list(c( "reference", "early"), 
                                  c( "early", "late"),
                                 c( "reference", "late")),
                map_signif_level=TRUE,
                textsize = 2, family = 'Helvetica',
                vjust = 0, size = 0.5, step_increase = 0.075) +
  labs(title = paste(whichtissue, sep = " "), subtitle = " ", y = NULL) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- df %>%
    dplyr::filter(gene  == whichgene)  %>%
      mutate(extint = factor(extint, levels = levelhypothesis)) %>%
    ggplot(aes(y =  counts, x = extint, fill = extint, color = sex)) +
    geom_boxplot(outlier.shape = NA, lwd=0.5) +
    #facet_wrap(~sex) +
    geom_jitter(size = 0.25, aes(color = treatment)) +
    theme_B3() +
  scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
  geom_signif(comparisons = list(c( "reference", "eggs"), 
                                  c( "eggs", "chicks"),
                                 c( "chicks", "loss"),
                                 c( "reference", "chicks"),
                                 c( "eggs", "loss"),
                                 c( "reference", "loss")),
                map_signif_level=TRUE,
                textsize = 2, family = 'Helvetica',
                vjust = 0, size = 0.5, step_increase = 0.075) +
  labs(title = " ", subtitle = " " , y = NULL) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1))

p <- plot_grid(p1,p2)
return(p)
}

a <- plotcandidatemanp(hypvsdf, "HTR2C", "female hypothalamus") 
b <- boxplotextint(hypvsdf, "HTR2C", " ") 
c <- plotcandidatemanp(hypvsdm, "HTR2C", "male hypothalamus") 
d <- boxplotextint(hypvsdm, "HTR2C", " ")

e <- plotcandidatemanp(pitvsdf, "PRL", "female pituitary")
f <- boxplotextint(pitvsdf, "PRL", " ")

g <- plotcandidatemanp(pitvsdm, "PRL", "male pituitary")
h <- boxplotextint(pitvsdm, "PRL", " ")

i <- plotcandidatemanp(gonvsdf, "ESR2", "female gonads") 
j <- boxplotextint(gonvsdf, "ESR2", " ")

k <- plotcandidatemanp(gonvsdm, "ESR2", "male gonads") 
l <- boxplotextint(gonvsdm, "ESR2", " ")

fig3 <- plot_grid(a,b,c,d,e,f, 
                       g,h,i,j,k,l, rel_widths = c(1.75,1,1.75,1),
                       labels = c("A", "", "", "", 
                                  "B", "", "", "", 
                                  "C", "", "", ""),
                       label_size = 8, hjust = 0)
fig3
```

## write files

```{r write}

pdf(file="../figures/fig3-1.pdf", width=7.25, height=7.25)
plot(fig3)
dev.off()

write.csv(candidatevsd, "../results/fig3-suppltable.csv")

```
